An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-30 EconGrowthSeminar.Rnw
A few small edits on the seminar presentation.

    \footnotesize
    No known rigorous, statistical comparative studies of economic growth models for various types of economies. 
    \normalsize
    \pause
    \vspace{\baselineskip}

    Extra credit: reflect dynamics of energy cost share and prices spikes.
  \end{center}
\end{frame}

@@

    \item{Labor ($L$): workers in an economy (people or hours)}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Comments on Cobb-Douglas Model Equation} %----------------------------
  \begin{center} \cdeEqn \end{center}
  \begin{itemize}
    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
    \begin{itemize}
      \item{Represents the ``irrepressible'' ``progress'' of technology}
      \item{Is independent of factors of production ($k$, $l$, and $e$)}
    \end{itemize}
    \item{$k$, $l$, and $e$ factors of production ``blend'' with $\alpha + \beta + \gamma = 1$}
    \item{Example: \citet{Froling:2009vo}}
  \end{itemize}
\end{frame}

@@

@@

\begin{frame}{Tentative Conclusions} %----------------------------
  \begin{itemize}
  \item{Including energy in Cobb-Douglas and CES production functions is unwarranted \\
        \scriptsize
        Preliminary statistical evidence indicates that energy parameters are not significant for most countries \\Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$), so including energy is unnecessary.
        \normalsize}
  \item{Including energy in LINEX production function is required \\
        \scriptsize
        The foundation of LINEX is an energy term.\\Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries.\\However, LINEX fits are worse overall than Cobb-Douglas or CES.
        \normalsize}
  \end{itemize}
\end{frame}

@@

    \pause
    Answer: Cobb-Douglas without energy or CES 
  \end{center}
\end{frame}

\begin{frame}{Extra Credit?} %----------------------------
  \begin{itemize}
    \item{Price, cost share exogenous to all models}
    \pause
    \item{Models (CD without energy, CES) could be \emph{included within} a model that endogenizes price and cost share}
    \pause
    \item{Still searching for a modeling approach that captures price and cost share dynamics \\ \scriptsize System dynamics modeling? \normalsize}
    \pause
    \item{No extra credit!}
  \end{itemize}
\end{frame}

>>>>

    \footnotesize
    No known statistically-rigorous comparative studies of economic growth models for various types of economies. 
    \normalsize
    \pause
    \vspace{\baselineskip}

    Extra credit: reflect dynamics of energy cost share and price spikes.
  \end{center}
\end{frame}

@@

    \item{Labor ($L$): human work in an economy (people or hours)}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Comments on Cobb-Douglas Model Equation} %----------------------------
  \begin{center} \cdeEqn \end{center}
  \begin{itemize}
    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
    \item{$k$, $l$, and $e$ factors of production ``blend'' with $\alpha + \beta + \gamma = 1$}
    \item{Example: \citet{Froling:2009vo}}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Tentative Conclusions} %----------------------------
  \begin{itemize}
  \item{Including energy in Cobb-Douglas and CES production functions is unwarranted \\
        \scriptsize
        Preliminary statistical evidence indicates that energy parameters are not significant for most countries \\Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$).
        \normalsize}
  \item{Including energy in LINEX production function is required \\
        \scriptsize
        The foundation of LINEX is an energy term.\\Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries.\\However, LINEX fits are worse overall than Cobb-Douglas or CES.
        \normalsize}
  \end{itemize}
\end{frame}

@@

@@

    \pause
    Answer: Cobb-Douglas or CES without energy
  \end{center}
\end{frame}

\begin{frame}{Extra Credit?} %----------------------------
  \begin{center} Reflect dynamics of energy cost share and price spikes \end{center}
    \vspace{\baselineskip}

    \pause
  \begin{itemize}
    \item{Price, cost share exogenous to all models}
    \pause
    \item{Models (CD and CES without energy) could be \emph{included within} a model that endogenizes price and cost share}
    \pause
    \item{Still searching for a modeling approach that captures price and cost share dynamics \\ \scriptsize System dynamics modeling? \normalsize}
    \pause
    \item{No extra credit!}
  \end{itemize}
\end{frame}
